Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-26 paper/structureScene.tex
write intro of section IV

>>>>

\section{Feature design}
Prior to supervised or unsupervised classification, is it beneficial to process scattering coefficients with feature transformations that improve invariance, normality, or generalization power. 
This section reviews binaural data augmentation, feature selection, logarithmic compression, standardization, and temporal integration.
The former is novel and specific to stereophonic recordings, whereas the next ones would also apply to many other problems.
